Impact of Education on Entrepreneurship - Data Gathering and Analysis

### 2014-11-14 GEMDataSource.Rmd
Final commit for assignment 3, minor text
Corrected spelling error

Going forward, we are considering adding one oof the six questions used by GEM to measure the importance of entrepreneurial education at the country level in its NES Survey.  Item D01 states "in my country, teaching in primary and secondary education encourages creativity, self-sufficiency, and personal initiative." This could be a proxy to get a sense of how supportive of self esteem a given education system is.

>>>>

Going forward, we are considering adding one of the six questions used by GEM to measure the importance of entrepreneurial education at the country level in its NES Survey.  Item D01 states "in my country, teaching in primary and secondary education encourages creativity, self-sufficiency, and personal initiative." This could be a proxy to get a sense of how supportive of self esteem a given education system is.
